Overview

### 2019-03-17 notebooks/general_info.Rmd
small additions to the code. date lookup was not impressive, but i used classes---dates show up in class info in a few ways---and not too much overlap was there. mind you, some arguments still claim that they are dates, even without class info to corroborate. ill dig deeper

>>>>

73% coincide.
Nice.
Dates might be another possibility?
Let's check:

```{r}
sigs_with_real_char <- get_fun_sigs_matching_pred_from_lopkg(los_basic_no_null_real_primitive_class, does_df_have_X_types, types_to_find=c("real", "character"), strict=TRUE)
```

```{r}
sigs_with_dates <- get_fun_sigs_matching_pred_from_lopkg(los_basic_no_null_real_primitive_class, does_df_have_date_real_char)
```

Hmm... Not as much as we would have liked, just 20% of the leftover (or 5% of the total).
Why don't we just see what's leftover:
```{r}
just_index <- get_fun_sigs_matching_pred_from_lopkg(los, does_df_have_coinciding_types_index_and_NOT_list_or_vector)
```

This isn't working the way I was expecting.
